Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience

### 2016-04-25 paper.tex
Modifies Makefile to do smaller pieces at each step Modifies paper to use tables for the sets of graphs Removes unnecessarily copied source files

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Loop Device Performance Overhead for Constraining Batch Job Tasks}

@@

\subsection{Performance}
The results presented in subsequent pages display the median value across each nest depth with the respective median absolute deviation. This format was chosen in order to present the most accurate representation of loop device performance. The performance of a loop device mounted with the any of the ext family filesystems performs comparably in many cases with the native filesystem. The native filesystem of our test platform is ext4. By using non-trivial sizes for the test allocations (in the order of GBs), our micro-benchmarks simulate sustained I/O expected of a batch job task completing a realistic work load. This is opposed to burst I/O which would be seen in tasks smaller than 1GB.

@@

\newpage
\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext2_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext2_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext2_2GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext2 Filesystem with 2GB Allocations}
	\label{fig:loop_ext2_2gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext3_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext3_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext3_2GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext3 Filesystem with 2GB Allocations}
	\label{fig:loop_ext3_2gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext4_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext4_2GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext4_2GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext4 Filesystem with 2GB Allocations}
	\label{fig:loop_ext4_2gb}
\end{figure*}

\clearpage
\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext2_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext2_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext2_4GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext2 Filesystem with 4GB Allocations}
	\label{fig:loop_ext2_4gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext3_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext3_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext3_4GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext3 Filesystem with 4GB Allocations}
	\label{fig:loop_ext3_4gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext4_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext4_4GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext4_4GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext4 Filesystem with 4GB Allocations}
	\label{fig:loop_ext4_4gb}
\end{figure*}

\clearpage
\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext2_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext2_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext2_8GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext2 Filesystem with 8GB Allocations}
	\label{fig:loop_ext2_8gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext3_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext3_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext3_8GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext3 Filesystem with 8GB Allocations}
	\label{fig:loop_ext3_8gb}
\end{figure*}

\begin{figure*}[t]
\begin{center}$
\begin{array}{ccc}
	\includegraphics[width=0.3\textwidth]{read_ext4_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{write_ext4_8GB.pdf}&
	\includegraphics[width=0.3\textwidth]{meta_ext4_8GB.pdf}
\end{array}$
\end{center}
	\caption{Loop Device Performance of ext4 Filesystem with 8GB Allocations}
	\label{fig:loop_ext4_8gb}
\end{figure*}
% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{blindtext, graphicx}
\usepackage{amsmath}
\usepackage{algorithmic}
\usepackage{framed}
\usepackage{floatrow}
\usepackage{comment}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Loop Device Performance Overhead for Constraining Batch Job Tasks:\\A Technical Report and Experiment in Metascience}

@@

\subsection{Performance}
The results presented in Figures \ref{fig:2gb}, \ref{fig:4gb}, and \ref{fig:8gb} display the median value across each nest depth with the respective median absolute deviation. This format was chosen in order to present the most accurate representation of loop device performance. The performance of a loop device mounted with the any of the ext family filesystems performs comparably in many cases with the native filesystem. The native filesystem of our test platform is ext4. By using non-trivial sizes for the test allocations (in the order of GBs), our micro-benchmarks simulate sustained I/O expected of a batch job task completing a realistic work load. This is opposed to burst I/O which would be seen in tasks smaller than 1GB.

@@

\newpage
\newcommand{\cimage}[1]{$\vcenter{\hbox{\includegraphics[width=0.3\textwidth]{#1}}}$}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_2GB.pdf} & \cimage{write_ext2_2GB.pdf} & \cimage{meta_ext2_2GB.pdf}\\
ext3 & \cimage{read_ext3_2GB.pdf} & \cimage{write_ext3_2GB.pdf} & \cimage{meta_ext3_2GB.pdf}\\
ext4 & \cimage{read_ext4_2GB.pdf} & \cimage{write_ext4_2GB.pdf} & \cimage{meta_ext4_2GB.pdf}\\
\end{tabular}
\label{fig:2gb}
\caption{Loop Device Performance with 2GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_4GB.pdf} & \cimage{write_ext2_4GB.pdf} & \cimage{meta_ext2_4GB.pdf}\\
ext3 & \cimage{read_ext3_4GB.pdf} & \cimage{write_ext3_4GB.pdf} & \cimage{meta_ext3_4GB.pdf}\\
ext4 & \cimage{read_ext4_4GB.pdf} & \cimage{write_ext4_4GB.pdf} & \cimage{meta_ext4_4GB.pdf}\\
\end{tabular}
\label{fig:4gb}
\caption{Loop Device Performance with 4GB Allocations}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{cccc}
ext2 & \cimage{read_ext2_8GB.pdf} & \cimage{write_ext2_8GB.pdf} & \cimage{meta_ext2_8GB.pdf}\\
ext3 & \cimage{read_ext3_8GB.pdf} & \cimage{write_ext3_8GB.pdf} & \cimage{meta_ext3_8GB.pdf}\\
ext4 & \cimage{read_ext4_8GB.pdf} & \cimage{write_ext4_8GB.pdf} & \cimage{meta_ext4_8GB.pdf}\\
\end{tabular}
\label{fig:8gb}
\caption{Loop Device Performance with 8GB Allocations}
\end{figure*}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi
